\thesistitle

### 2019-07-24 sections/background.tex
Table

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} &  & - \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these code fragments\\is called a ``clone instance''.\end{tabular} &  & - \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \ref{jiang2007deckard}& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} &  & \textbf{Range:} The range this node spans. \\
\rowcolor[HTML]{EFEFEF}
T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

>>>>

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these code fragments\\is called a ``clone instance''.\end{tabular} &  & - \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \ref{jiang2007deckard}& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} &  & \textbf{Range:} The range this node spans. \\
\rowcolor[HTML]{EFEFEF}
T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}
